\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-07-30 tex/ms.tex
fixes
more general r param

%
\section{The Spot Expansion}
\label{sec:spot}
%
\subsection{Preliminaries}
%
We adopt the following expression for the spherical harmonic coefficient
of degree $l$ and order $m$ in the expansion of a spot at
$\theta = \varphi = 0$:
%
\begin{align}
    \label{eq:ylm0}
    y_{lm}(r, \delta) =
    \begin{cases}
        1 - \dfrac{\delta c r}{2 (1 + c r)}
         & l = m = 0    \\[2em]
        -\dfrac{\delta c r \left( 2 + c r \right)}
        {2 \sqrt{2l + 1} (1 + c r)^{l + 1}}
         & l > 0, m = 0 \\[2em]
        0
         & m \ne 0
    \end{cases}
\end{align}
%
where $\delta \in [-\infty, 1]$ is the spot contrast (the fractional
decrease in the brightness
at the center of the spot) and $r \in (0, 1]$ is the normalized spot radius.
The quantity $c \in (0, \infty)$ is a normalization constant for the radius
(more details below).
The expression in Equation~(\ref{eq:ylm0}) is convenient because it satisfies
four important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $1 - \delta$
    \item The surface intensity at the antipode of the spot center is unity
    \item The size of the spot increases monotonically with $r$
\end{enumerate}
%
These properties may be demonstrated by considering the expression for the
surface intensity at a given point $(\theta, \varphi)$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{l=0}^\infty \sum\limits_{m=-l}^l
        y_{lm} Y_{lm}(\theta, \varphi) \\
        & = \sum\limits_{l=0}^\infty
        y_{l0} \sqrt{2l + 1} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $P_l$ is the Legendre polynomial of degree $l$ and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Combining this with Equation~(\ref{eq:ylm0}) and rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    1 + \dfrac{\delta c r}{2}
    -
    \dfrac{\delta c r \left( 2 + c r \right)}{2 (1 + c r)}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + c r}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta, \varphi) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = 1 + \dfrac{\delta c r}{2}                      \\
        B & = \delta c r (2 + cr) \sqrt{\dfrac{1}{8 + 8 cr}} \\
        C & = \dfrac{1 + (1 + c r)^2}{2 + 2 c r}
    \end{split}
\end{align}
%
are positive constants.

Differentiating Equation~(\ref{eq:Ifinal}) with respect to $\theta$, we have
%
\begin{align}
    \label{eq:Ideriv}
    \dfrac{\mathrm{d}I(\theta, \varphi)}{\mathrm{d}\theta} & =
    -\frac{B\sin\theta}{2(C - \cos\theta)^\frac{3}{2}}
    \quad,
\end{align}
%
which is zero only for $\theta = 0$ (for which $I(\theta, \varphi)$ is
minimized) and $\theta = \pi$ (for which it is maximized). The intensity
therefore increases monotonically from the spot center to the antipode,
as stated in \textbf{1}. The value at the minimum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{min}} & = A - \dfrac{B}{\sqrt{C - 1}} \\
        & = 1 - \delta
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{2}, and the value at the maximum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{max}} & = A - \dfrac{B}{\sqrt{C + 1}} \\
        & = 1
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{3}.
Finally, to show \textbf{4}, let us compute the half width at half minimum
$\Delta\theta$ of the intensity profile:
%
\begin{align}
    1 - \left(A - \dfrac{B}{\sqrt{C - \cos{\Delta\theta}}}\right) =
    \dfrac{1}{2}\delta
\end{align}
%
Solving for $\Delta\theta$ yields
%
\begin{align}
    \Delta\theta =
    \cos^{-1} \left[ \dfrac{2 + 3 c r (2 + c r)}{2 (1 + c r)^3} \right]
    \quad.
\end{align}
%
Differentiation with respect to $r$ yields
%
\begin{align}
    \dfrac{\mathrm{d}\Delta\theta}{\mathrm{d}r} =
    \frac{3 c^2 r \left(2 + c r\right)}{\left(1 + c r\right)^4
        \sqrt{\frac{c^2 r^2 \left(2 + c r\right)^2 \left(1 + 2 c r\right)
                \left(3 + 2 c r\right)}{\left(1 + c r\right)^6}}}
    \quad,
\end{align}
%
which is positive definite for all $c, r > 0$.

\subsection{Distributions over $r$ and $\delta$}
%
We model the normalized spot radius $r$ as a random variable drawn from
a Beta distribution, whose PDF is given by
%
\begin{align}
    p \big(r \, \big| \, \alpha, \beta \big)
     & =
    \dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
    r^{\alpha - 1}
    (1 - r)^{\beta - 1}
    \quad,
\end{align}
%
where $\Gamma$ is the Gamma function and $\alpha$ and $\beta$ are
hyperparameters characterizing the shape of the distribution.
%
Since we require the brghtness $b = 1 - \delta$ at the center of the spot to
be non-negative, it is convenient to parametrize the distribution of $b$
instead of $\delta$. We model $b$ as a random variable drawn from a log-normal
distribution:
%
\begin{align}
    p \big(b \, \big| \, \mu, \nu \big)
     & =
    \frac{1}{b\sqrt{2\pi\nu}}
    \exp\left[
        -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
        \right]
    \quad,
\end{align}
%
where $\mu$ and $\nu$ are the mean and variance of the log-normal, respectively.
The joint distribution over $r$ and $b$ is therefore separable,
by construction:
%
\begin{align}
    p \big( r, b \, \big| \, \alpha, \beta, \mu, \nu \big)
     & =
    p \big(r \, \big| \, \alpha, \beta \big)
    \,
    p \big(b \, \big| \, \mu, \nu \big)
    \quad.
\end{align}
%

@@

@@

        1 - \dfrac{(1 - b) c r}{2 (1 + c r)}

@@

        \dfrac{(1 - b) c r \left( 2 + c r \right)r^{\alpha - 1}

@@

        {2 \sqrt{2l + 1} (1 + c r)^{l + 1}}

@@

@@

powers of $r$ and $(1 + cr)$, the integrals above may be expressed in closed

@@

        \dfrac{(1 - b) \alpha c}{2(\alpha + \beta)} F_l

@@

        -\dfrac{(1 - b) \alpha c}{\sqrt{2l + 1} (\alpha + \beta)}
        \left[
            F_l + \dfrac{(\alpha + 1)c}{2(\alpha + \beta + 1)} G_l
            \right]

@@

        F_l & \equiv {_2F_1}(l + 1, \alpha + 1; \alpha + \beta + 1; -c)
        \\[1em]
        G_l & \equiv {_2F_1}(l + 1, \alpha + 2; \alpha + \beta + 2; -c)

@@

@@

$F_0$, $F_1$, $G_0$, and $G_1$ directly, since the remaining terms may be

@@

        F_l &=
        \dfrac{\alpha + \beta + 1 - l}{2l}F_{l - 2}
        - \dfrac{2\alpha + \beta + 2 - 3l}{2l}F_{l - 1}
        \\[1em]
        G_l &=
        \dfrac{\alpha + \beta + 2 - l}{2l}G_{l - 2}
        - \dfrac{2\alpha + \beta + 4 - 3l}{2l}G_{l - 1}

@@

We may now evaluate the integral in Equation~(\ref{eq:Erb}):

@@

    \mathrm{E} \big[ y_{lm} \big] & =
        \frac{1}{b\sqrt{2\pi\nu}}
        \dfrac{(1 - b) \alpha c}{2(\alpha + \beta)} F_l
        \qquad\qquad\times
        \exp\left[
            -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
            \right]
        \qquad\qquad
        l = m = 0
        \frac{1}{b\sqrt{2\pi\nu}}
        \dfrac{(1 - b) \alpha c}{\sqrt{2l + 1} (\alpha + \beta)}
        \qquad\qquad\times
        \left[
            F_l + \dfrac{(\alpha + 1)c}{2(\alpha + \beta + 1)} G_l
            \right]
        \qquad\qquad\times
        \exp\left[
            -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
            \right]
        \qquad\qquad
        \qquad\qquad m \ne 0
Most of the terms in the integrands above are constants, so these
integrals may also be expressed in closed form:

@@

        \dfrac{\gamma \alpha c}{2(\alpha + \beta)} F_l

@@

        -\dfrac{\gamma \alpha c}{\sqrt{2l + 1} (\alpha + \beta)}
        \left[
            F_l + \dfrac{(\alpha + 1)c}{2(\alpha + \beta + 1)} G_l
            \right]

@@

    \gamma \equiv 1 - \exp\left[ \mu + \frac{1}{2}\nu\right]

@@

\subsection{Second moment}
%
The second moment of the distribution of $y_{lm}$ over $r$ and $b$ is
%
\begin{align}
    \label{eq:Erb2}
    \begin{split}
        \mathrm{E} \big[ y_{lm} y_{l'm'} \big] &=
        \int\limits_0^\infty \int\limits_0^1
        y_{lm} (r, 1 - b)
        y_{l'm'} (r, 1 - b)
        p \big(r, 1 - b \, \big| \, \alpha, \beta, \mu, \nu \big)
        \mathrm{d} r
        \,
        \mathrm{d} b
        \\
        &=
        \int\limits_0^\infty
        \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
        p \big(b \, \big| \, \mu, \nu \big)
        \mathrm{d} b
        \quad,
    \end{split}
    %
    \\
    \intertext{where}
    \label{eq:Er2}
    %
    \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
     & =
    \int\limits_0^1
    y_{lm} (r, 1 - b)
    y_{l'm'} (r, 1 - b)
    p \big(r \, \big| \, \alpha, \beta \big)
    \mathrm{d} r
    \quad.
\end{align}
%
Expanding Equation~(\ref{eq:Er2}), we obtain
%
\begin{align}
    \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
     & =
    \begin{dcases}
        \dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
        \int\limits_0^1
        \left(
        1 - \dfrac{(1 - b) c r}{2 (1 + c r)}
        \right)^2
        r^{\alpha - 1}
        (1 - r)^{\beta - 1}
        \mathrm{d} r
         &
        \quad\quad
        \parbox[t]{\linewidth}{$l = l',              \\m = m' = 0$}
        \\[2em]
        %
        -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
        \int\limits_0^1
        \left(1 - \dfrac{(1 - b) c r}{2 (1 + c r)}\right)
        \\
        \qquad\qquad\quad\quad\times
        \dfrac{(1 - b) c r \left( 2 + c r \right) r^{\alpha - 1}
            (1 - r)^{\beta - 1}}
        {2 \sqrt{2l + 1} (1 + c r)^{l + 1}}
        \mathrm{d} r
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-3em}$l > 0,  \\l' = 0, \\m = m' = 0$}
        \\[2em]
        %
        -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
        \int\limits_0^1
        \left(1 - \dfrac{(1 - b) c r}{2 (1 + c r)}\right)
        \\
        \qquad\qquad\quad\quad\times
        \dfrac{(1 - b) c r \left( 2 + c r \right) r^{\alpha - 1}
            (1 - r)^{\beta - 1}}
        {2 \sqrt{2l' + 1} (1 + c r)^{l' + 1}}
        \mathrm{d} r
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-3em}$l = 0,  \\l' > 0, \\m = m' = 0$}
        \\[2em]
        %
        -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
        \int\limits_0^1
        \dfrac{(1 - b)^2 c^2 r^2 \left( 2 + c r \right)^2 r^{\alpha - 1}
            (1 - r)^{\beta - 1}}
        {4 \sqrt{(2l + 1)(2l' + 1)} (1 + c r)^{l + l' + 2}}
        \mathrm{d} r
         &
        \quad\quad
        \parbox[t]{\linewidth}{\vspace{-1.5em}$l > 0 \\l' > 0 \\m = m' = 0$}
        \\[2em]
        %
        0
         &
        \quad\quad m, m' \ne 0
        \quad.
    \end{dcases}
\end{align}

>>>>

%
\section{The Spot Expansion}
\label{sec:spot}
%
\subsection{Preliminaries}
%
We adopt the following expression for the spherical harmonic coefficient
of degree $l$ and order $m$ in the expansion of a spot at
$\theta = \varphi = 0$:
%
\begin{align}
    \label{eq:ylm0}
    y_{lm}(r, \delta) =
    \begin{cases}
        1 - \dfrac{\delta r'}{2 (1 + r')}
         & l = m = 0    \\[2em]
        -\dfrac{\delta r' \left( 2 + r' \right)}
        {2 \sqrt{2l + 1} (1 + r')^{l + 1}}
         & l > 0, m = 0 \\[2em]
        0
         & m \ne 0
    \end{cases}
\end{align}
%
where
%
\begin{align}
    \label{eq:rprime}
    r' \equiv c_0 + c_1 r
\end{align}
%
and $c_0, c_1 > 0$ are scaling constants (defined in more detail below).
In the expressions above,
$\delta \in (-\infty, 1]$ is the spot contrast (the fractional
decrease in the brightness
at the center of the spot) and $r \in [0, 1]$ is the normalized spot radius.
The expression in Equation~(\ref{eq:ylm0}) is convenient because it satisfies
five important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity is azimuthally symmetric about the spot center
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $1 - \delta$
    \item The surface intensity at the antipode of the spot center is unity
    \item The size of the spot increases monotonically with $r$
\end{enumerate}
%
These properties may be demonstrated by considering the expression for the
surface intensity at a given point $(\theta, \varphi)$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{l=0}^\infty \sum\limits_{m=-l}^l
        y_{lm} Y_{lm}(\theta, \varphi) \\
        & = \sum\limits_{l=0}^\infty
        y_{l0} \sqrt{2l + 1} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $P_l$ is the Legendre polynomial of degree $l$ and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Note that the expression above is independent of the azimuth $\varphi$,
a consequence of the fact that all harmonics with $m \ne 0$ are zero; this
expansion is therefore azimuthally symmetric about the spot center, as
stated in \textbf{1}.
%
Combining the above expression with Equation~(\ref{eq:ylm0}) and
rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    I(\theta) =
    1 + \dfrac{\delta r'}{2}
    -
    \dfrac{\delta r' \left( 2 + r' \right)}{2 (1 + r')}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + r'}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = 1 + \dfrac{\delta r'}{2}                      \\
        B & = \delta r' (2 + r') \sqrt{\dfrac{1}{8 + 8 r'}} \\
        C & = \dfrac{1 + (1 + r')^2}{2 + 2 r'}
    \end{split}
\end{align}
%
are positive constants.

Differentiating Equation~(\ref{eq:Ifinal}) with respect to $\theta$, we have
%
\begin{align}
    \label{eq:Ideriv}
    \dfrac{\mathrm{d}I(\theta)}{\mathrm{d}\theta} & =
    -\frac{B\sin\theta}{2(C - \cos\theta)^\frac{3}{2}}
    \quad,
\end{align}
%
which is zero only for $\theta = 0$ (for which $I(\theta)$ is
minimized) and $\theta = \pi$ (for which it is maximized). The intensity
therefore increases monotonically from the spot center to the antipode,
as stated in \textbf{2}. The value at the minimum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{min}} & = A - \dfrac{B}{\sqrt{C - 1}} \\
        & = 1 - \delta
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{3}, and the value at the maximum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{max}} & = A - \dfrac{B}{\sqrt{C + 1}} \\
        & = 1
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{4}.
Finally, to show \textbf{5}, let us compute the half width at half minimum
$\Delta\theta$ of the intensity profile:
%
\begin{align}
    1 - \left(A - \dfrac{B}{\sqrt{C - \cos{\Delta\theta}}}\right) =
    \dfrac{1}{2}\delta
\end{align}
%
Solving for $\Delta\theta$ yields
%
\begin{align}
    \Delta\theta =
    \cos^{-1} \left[ \dfrac{2 + 3 r' (2 + r')}{2 (1 + r')^3} \right]
    \quad.
\end{align}
%
Differentiation with respect to $r'$ yields
%
\begin{align}
    \dfrac{\mathrm{d}\Delta\theta}{\mathrm{d}r'} =
    \frac{3 r' \left(2 + r'\right)}{\left(1 + r'\right)^4
        \sqrt{\frac{r'^2 \left(2 + r'\right)^2 \left(1 + 2 r'\right)
                \left(3 + 2 r'\right)}{\left(1 + r'\right)^6}}}
    \quad,
\end{align}
%
which is positive definite for all $r' > 0$.

\subsection{Distributions over $r$ and $\delta$}
%
We model the normalized spot radius $r$ as a random variable drawn from
a Beta distribution, whose PDF is given by
%
\begin{align}
    p \big(r \, \big| \, \alpha, \beta \big)
     & =
    \dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
    r^{\alpha - 1}
    (1 - r)^{\beta - 1}
    \quad,
\end{align}
%
where $\Gamma$ is the Gamma function and $\alpha$ and $\beta$ are
hyperparameters characterizing the shape of the distribution.
%
Since we require the brightness
%
\begin{align}
    b \equiv 1 - \delta
\end{align}
%
at the center of the spot to
be non-negative, it is convenient to treat $b \in [0, \infty)$ as our
random variable instead of $\delta$. We model $b$ as a random variable
drawn from a log-normal
distribution:
%
\begin{align}
    \label{eq:lognormal}
    p \big(b \, \big| \, \mu, \nu \big)
     & =
    \frac{1}{b\sqrt{2\pi\nu}}
    \exp\left[
        -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
        \right]
    \quad,
\end{align}
%
where $\mu$ and $\nu$ are the mean and variance of the log-normal, respectively.
The joint distribution over $r$ and $b$ is therefore separable,
by construction:
%
\begin{align}
    p \big( r, b \, \big| \, \alpha, \beta, \mu, \nu \big)
     & =
    p \big(r \, \big| \, \alpha, \beta \big)
    \,
    p \big(b \, \big| \, \mu, \nu \big)
    \quad.
\end{align}
%

@@

    \resizebox{.75\hsize}{!}{$

@@

                1 - \dfrac{(1 - b) (c_0 + c_1 r)}{2 (1 + c_0 + c_1 r)}

@@

                \dfrac{(1 - b) (c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)r^{\alpha - 1}

@@

                {2 \sqrt{2l + 1} (1 + c_0 + c_1 r)^{l + 1}}

@@

        $}

@@

powers of $r$ and $(1 + c_0 + c_1 r)$, the integrals above may be expressed in closed

@@

                \dfrac{(1 - b)}{2(1 + c_0)}
                \bigg[c_0H_0^0 + c_1 H_0^1\bigg]

@@

                -\dfrac{(1 - b)}{2\sqrt{2l + 1} (1 + c_0)^{l+1}}
                \bigg[
                    c_0(2+c_0)H_l^0
                    +
                    2c_1(1 + c_0)H_l^1
                    +
                    c_1^2 H_l^2
                    \bigg]

@@

    H_j^k & \equiv \left(\prod_{n=0}^{k-1} \lambda_n\right) G_j^k

@@

with
    \lambda_n & \equiv \dfrac{\alpha + n}{\alpha + \beta + n}
and
    G_j^k & \equiv {_2F_1}\left(j + 1, \alpha + k; \alpha + \beta + k; -\dfrac{c_1}{1 + c_0}\right)

@@

$G_0^0$, $G_1^0$, $G_0^1$, and $G_1^1$ directly, since the remaining terms may be

@@

    \label{eq:Grec}
    G_j^k & =
    \dfrac{\alpha + \beta + k - j}{2j}G_{j - 2}^k
    - \dfrac{2\alpha + \beta + 2k - 3j}{2j}G_{j - 1}^k

@@

\textbf{TODO: Recursion for k > 1.\\}

@@

We may now evaluate the integral in Equation~(\ref{eq:Erb}), with
PDF given by Equation~(\ref{eq:lognormal}).
Most of the terms in the integrands are constants, so the
integrals are straightforward to evaluate and may also
be expressed in closed form:

@@

                \dfrac{\gamma_1}{2(1 + c_0)}
                \bigg[c_0 H_0^0 + c_1 H_0^1\bigg]

@@

                -\dfrac{\gamma_1}{2\sqrt{2l + 1} (1 + c_0)^{l+1}}
                \bigg[
                    c_0(2+c_0)H_l^0
                    +
                    2c_1(1 + c_0)H_l^1
                    +
                    c_1^2 H_l^2
                    \bigg]

@@

    \gamma_1 \equiv 1 - \exp\left[ \mu + \frac{1}{2}\nu\right]

@@

\subsection{Second moment}
The second moment of the distribution of $y_{lm}$ over $r$ and $b$ is
    \label{eq:Erb2}
        \mathrm{E} \big[ y_{lm} y_{l'm'} \big] &=
        y_{l'm'} (r, 1 - b)
        \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
    \label{eq:Er2}
    \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
    y_{l'm'} (r, 1 - b)
Expanding Equation~(\ref{eq:Er2}), we obtain
    \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
    \resizebox{1.5\hsize}{!}{$
                1 - \dfrac{(1-b) (c_0 + c_1 r)}{2 (1 + c_0 + c_1 r)}
                \right)^2
                \qquad\qquad\quad\quad\quad\quad\quad
                \times
                \,\,
                \parbox[t]{\linewidth}{\vspace{-2.5em}$l = l' = 0, \\m = m' = 0$}
                \\[2em]
                1 - \dfrac{(1-b) (c_0 + c_1 r)}{2 (1 + c_0 + c_1 r)}
                \qquad\qquad\quad\quad\quad\quad\quad\quad\quad\quad\quad
                \times
                \dfrac{(1-b) (c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)}
                    {2 \sqrt{2l + 1} (1 + c_0 + c_1 r)^{l + 1}}
                \\[0.75em]
                \qquad\qquad\quad\quad\quad\quad\quad\quad\quad\quad\quad
                \times
                \,\,
                \parbox[t]{\linewidth}{\vspace{-5em}$l > 0,        \\l' = 0, \\m = m' = 0$}
                \\[2em]
                \dfrac{(1-b) (c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)}
                    {2 \sqrt{2l + 1} (1 + c_0 + c_1 r)^{l + 1}}
                \qquad\qquad\quad\quad\quad\quad\quad\quad\quad\quad\quad
                \times
                \dfrac{(1-b) (c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)}
                    {2 \sqrt{2l' + 1} (1 + c_0 + c_1 r)^{l' + 1}}
                \\[0.75em]
                \qquad\qquad\quad\quad\quad\quad\quad\quad\quad\quad\quad
                \times
                \,\,
                \parbox[t]{\linewidth}{\vspace{-5em}$l > 0,        \\l' > 0, \\m = m' = 0$}
                \\[2em]
                \qquad m, m' \ne 0
        $}
    \raisetag{14.5em}
where, by symmetry, the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is the same as
in the second case, provided we make the substitution $l \rightarrow l'$.
These integrals again reduce to closed form expressions:
    \mathrm{E}_r \big[ y_{lm} y_{l'm'} \big]
    \resizebox{1.4\hsize}{!}{$
                1 + \dfrac{1-b}{1+c_0}
                \bigg[
                    -c_0 H_0^0
                    c_1 H_0^1
                    \\[0.75em]
                \qquad\qquad\enspace\enspace\quad\quad
                +
                \dfrac{1-b}{2(1+c_0)}
                \bigg(
                \dfrac{c_0^2}{2}H_1^0
                +
                c_0 c_1 H_1^1
                +
                \dfrac{c_1^2}{2} H_1^2
                \bigg)
                \bigg]
                \parbox[t]{\linewidth}{\vspace{-3.5em}$l = l' = 0, \\m = m' = 0$}
                \\[2em]
                \dfrac{1-b}{2\sqrt{2l + 1}(1+c_0)^{l+1}}
                \\[0.75em]
                \enspace\quad
                \times
                \bigg[
                    c_0(2 + c_0) H_l^0 + 2 c_1(1 + c_0) H_l^1
                    + c_1^2 H_l^2
                    \\[0.75em]
                - \dfrac{1 - b}{2(1 + c_0)} \bigg(
                c_0^2(2 + c_0) H_{l+1}^0
                + c_0 c_1 (4 + 3 c_0) H_{l+1}^1
                \\[0.75em]
                + (2 + 3 c_0) c_1^2 H_{l + 1}^2
                + c_1^3 H_{l + 1}^3
                \bigg)
                \bigg]
                \parbox[t]{\linewidth}{\vspace{-7em}$l > 0,        \\l' = 0, \\m = m' = 0$}
                \\[2em]
                \dfrac{(1 - b)^2}{4\sqrt{(2l + 1)(2l' + 1)}(1+c_0)^{l+l'+2}}
                \\[0.75em]
                \enspace\quad
                \times
                \bigg[
                    c_0^2(2+c_0)^2 H_{l + l' + 1}^0
                    + 4 c_0 (1 + c_0) (2 + c_0) c_1 H_{l + l' + 1}^1
                    \\[0.75em]
                + 2 \big(2 + 3 c_0 (2 + c_0)\big)c_1^2 H_{l + l' + 1}^2
                + 4(1 + c_0)c_1^3 H_{l + l' + 1}^3
                \\[0.75em]
                + c_1^4 H_{l + l' + 1}^4
                \bigg]
                \parbox[t]{\linewidth}{\vspace{-5em}$l > 0,        \\l' > 0, \\m = m' = 0$}
        $}
    \raisetag{15em}
The final step is to evaluate the integral in Equation~(\ref{eq:Er2}), given
the PDF in Equation~(\ref{eq:lognormal}):
    \mathrm{E} \big[ y_{lm} y_{l'm'} \big]
    ?
    \gamma_2 \equiv 1
    - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]
and the expression for $l' > 0, \, l = 0, \, m = m' = 0$ is again the same as in
the second case, provided we make the substitution $l \rightarrow l'$.
